A Taxonomy of Twists of Supersymmetric Yang--Mills Theories

### 2020-01-27 paper.tex
in the middle
starting (1,2)

\subsubsection{Rank (2, 1) twist}

\begin{theorem}
\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.  However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}

>>>>

\subsubsection{Rank $(1, 2)$ twist}

Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$.

We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
\]
Notice the two scalar supercharges $Q_0, \Bar{Q}_0$, both of which are rank $(1,0)$.

Further, the representation $S_- \otimes W$ decomposes under $\MU(2)$ as
\[
S_- \otimes W^* = L \otimes L^*  \oplus L \oplus L \otimes \det(L)^{-1} .
\]
Within the first summand of $S_- \otimes W^*$ there is the trivial representation $\CC \cdot Q' \subset L \otimes L^*$ consisting of multiples of the identity endomorphism. 
The corresponding supercharge $Q'$ is of rank $(0,2)$.

The family of supercharges we consider is 
\begin{equation}\label{4d12hodge}
Q_t = Q_0 + t Q' .
\end{equation}
Since $Q_0, (Q')^*$ arise from different summands of $W$, the supercharges $Q_0, Q'$ commute. 
Hence $Q_t$ automatically squares to zero.

Notice that for $t \ne 0$ this family specializes to a rank $(1,2)$ supercharge.
When $t = 0$ the family specializes to the rank $(1,0)$ supercharge $Q_0$.

In the statement of the next proposition, we refer to the decomposition of fields of $4d \cN=4$ super Yang-Mills theory given in the proof of Theorem \ref{thm:4d4holomorphictwist}.

\begin{prop}
Suppose $Q_t$ is the rank $(1,2)$ supercharge of Equation \ref{4d12hodge}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(2)}_{\rm gauge}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
\brian{these formulas need to be fixed}
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
%I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
%I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
\end{align*}
\end{prop}

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{4d12hodge} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$. 
\brian{Pavel claims this is equivalent to $\map\left(\CC \times \RR^2_{\rm dR}, B\fg_{\Hod}\right)$}
Moreover, this equivalence is $\U(2)$-equivariant. \brian{Similarly, $\U(1) \times \U(1)$}
\label{thm:4d12hodge}
\end{theorem}
%
%\begin{theorem}
%\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.  However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
%\end{theorem}
